Ab Initio Effective One-Electron Potentials Revisited: General Theory and Example Applications for Charge-Transfer Energy Calculations

### 2019-11-29 papers/2_oep_technique.CT/paper-r0.tex
Adding pauli-repulsion paper

Until that point, the effective potentials from Eqs.~\eqref{e:oep-exch-like}
and \eqref{e:oep-coul-like} are not separable in terms of the interacting molecules
because the $\bf P$ tensors are derived from the CI wavefunction of
the entire interacting system $AB$. However, if there exist an approximate
separation as, for example,
%
\begin{align}
 P^{AAAB}_{mkij} &\approx X^A_{mk} Y^{AB}_{ij} \;, \\
 P^{AABB}_{ikjl} &\approx Z^A_{ik} Y^{AB}_{} Z^{ B}_{jl} \;,
\end{align}
%
and if the matrices ${\bf X}^{A(B)}$, 
${\bf Z}^{A(B)}$ and ${\bf P}^{AA(BB)}$ as well as the tensors
${\bf P}^{AAAA(BBBB)}$ 
are properties of the unperturbed (isolated) molecules,
further rearrangements in Eq.~\eqref{e:ci-oep-master} are possible
leading to computationally more efficient expressions.

>>>>

Until that point, the effective potentials from Eqs.~\eqref{e:oep-exch-like}
and \eqref{e:oep-coul-like} are not separable in terms of the interacting molecules
because the $\bf P$ tensors are derived from the CI wavefunction of
the entire interacting system $AB$. However, if there exist an approximate
separation as, for example,
%
\begin{align}
 P^{AB}_{ij} &\approx \sum_{k\in A} \sum_{l\in B} X^A_{ik} S_{kl}^{AB} X^B_{lj} \;,\\
 P^{AAAB}_{mkij} &\approx \sum_{k\in A} \sum_{l\in B} 
                 X^A_{mkik'} S^{AB}_{k'l'} Y^{B}_{l'j} \;, \\
 P^{AABB}_{ikjl} &\approx Z^A_{ik} Y^{AB}_{} Z^{ B}_{jl} \;,
\end{align}
%
and if the matrices ${\bf X}^{A(B)}$, 
${\bf Z}^{A(B)}$ and ${\bf P}^{AA(BB)}$ as well as the tensors
${\bf P}^{AAAA(BBBB)}$ 
are properties of the unperturbed (isolated) molecules,
further rearrangements in Eq.~\eqref{e:ci-oep-master} are possible
leading to computationally more efficient expressions.
